Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-06 grove-paper.tex
Move figures into commands (Michael D. Adams)
Fix spacing and various refinements to figures

%\selectcolormodel{gray}

@@

\usetikzlibrary{
  backgrounds,  % Provides "framed" and "gridded"
  graphs,       % Graph *notation*
  graphdrawing, % Graph *layout*
  quotes,       % Quote syntax (e.g., "foo")
}

@@

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  %color=gray,
  font={\footnotesize\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level distance=0.5cm,
  level sep=0.5cm,
  sibling distance=0.5cm,
  sibling sep=0.1cm,
  part distance=0.1cm,
  part sep=0.1cm,
  component distance=0.1cm,
  component sep=0.1cm,
  nodes={
    draw,
    %color=gray,
    inner sep=2pt,
    rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}
\tikzset{alice/.style={
  color=red!80!black,
  font={\bfseries\footnotesize},
  thick,
}}
\tikzset{bob/.style={
  color=green!60!black,
  font={\bfseries\footnotesize},
  thick,
}}
\tikzset{merge/.style={
  color=blue,
  font={\bfseries\footnotesize},
  thick,
}}
\tikzset{alice edge/.style={alice, edge style, font={\bfseries\footnotesize}}}
\tikzset{bob edge/.style={bob, edge style}, font={\bfseries\footnotesize}}
\tikzset{merge edge/.style={merge, edge style}, font={\bfseries\footnotesize}}

@@

>>>>

% \selectcolormodel{gray}

@@

\usetikzlibrary{
  backgrounds,  % Provides "framed" and "gridded"
  bending,      % bending arrow tips
  graphs,       % Graph *notation*
  graphdrawing, % Graph *layout*
  quotes,       % Quote syntax (e.g., "foo")
}

@@

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  %color=gray,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level distance=0.5cm,
  level sep=0.5cm,
  sibling distance=0.5cm,
  sibling sep=0.1cm,
  part distance=0.1cm,
  part sep=0.1cm,
  component distance=0.1cm,
  component sep=0.1cm,
  nodes={
    draw,
    %color=gray,
    inner sep=2pt,
    rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}
\tikzset{alice/.style={
  color=red!80!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{bob/.style={
  color=green!60!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{merge/.style={
  color=blue,
  font={\bfseries\small},
  thick,
}}
\tikzset{alice edge/.style={alice, edge style, font={\bfseries\small}}}
\tikzset{bob edge/.style={bob, edge style}, font={\bfseries\small}}
\tikzset{merge edge/.style={merge, edge style}, font={\bfseries\small}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole.
\autoref{fig:A simple tree with a hole-a}:~User interface.
\autoref{fig:A simple tree with a hole-b}:~Graph representation.}
\label{fig:A simple tree with a hole}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureConstructionAndDeletion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\newcommand{\figureConstructionAndDeletion}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-A simple tree with a hole-b-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:A simple tree with a hole-b}}}};
%%%%
\path (0cm,0cm) node (fig-Construction) [anchor=base] {\strut};
\path [draw,->,alice] (fig-A simple tree with a hole-b-x) to (-2em, 0cm |- fig-Construction);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-a}
\label{fig:Construction}
\label{fig:Construction-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY", >alice edge, alice]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Deletion) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Construction) to[alice edge] (-2em, 0cm |- fig-Deletion);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-b}
\label{fig:Change-a}
\label{fig:Change}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   {},
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\path (-0.25cm,-1.7cm) graph[graph style] {
 "\vSimpleX"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction and Deletion.}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureWrapping
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\newedge{WrapTimes}{L}
\newcommand{\figureWrapping}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-a) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Deletion) to[alice edge] (-2em, 0cm |- fig-Wrapping-a);
\end{tikzpicture}
}
\label{fig:Wrapping-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-b) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Wrapping-a) to[alice edge] (-2em, 0cm |- fig-Wrapping-b);
\end{tikzpicture}
}
\label{fig:Wrapping-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus", >alice edge, alice]
 }
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-c) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Wrapping-b) to[alice edge] (-2em, 0cm |- fig-Wrapping-c);
\end{tikzpicture}
}
\label{fig:Wrapping-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"', >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping.  Note that this figure omits the orphaned \Vertex{\vidSimpleX} since it is no longer relevant to our narrative.}
\label{fig:Wrapping}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMovement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MoveTimes}{R}
\newcommand{\figureMovement}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Wrapping-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Wrapping-c}}}};
%%%%
\path (0cm,0cm) node (fig-Moving-a) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Wrapping-c-x) to (-2em, 0cm |- fig-Moving-a);
\end{tikzpicture}
}
\label{fig:Move-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-1.7cm) graph [graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Moving-b) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Moving-a) to (-2em, 0cm |- fig-Moving-b);
\end{tikzpicture}
}
\label{fig:Move-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes", >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \vSimpleTimes{} to the right child of~\vWrapPlus{}.}
\label{fig:Move}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureEditingDifferentParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\newcommand{\figureEditingDifferentParts}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-a) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Moving-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-a);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >alice edge, alice],
    "\vConstructionY" [> "\eConstructionY"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-b) [anchor=base] {\strut};
\path [draw, bob,->] (fig-Moving-b) to [out=15,in=165] (-2em, 0cm |- fig-Editing Different Parts of the Code-b);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    {},
    "\vDifferentBob" [> "\eDifferentBob", >bob edge, bob]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-c) [anchor=base] {\strut};
\path [draw,->,merge] (fig-Editing Different Parts of the Code-a) to [out=15,in=165] (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\path [draw,->,merge] (fig-Editing Different Parts of the Code-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >merge edge, merge],
    "\vDifferentBob" [> "\eDifferentBob", >merge edge, merge]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code.}
\label{fig:Editing Different Parts of the Code}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureCommutativity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\figureCommutativity}{
\begin{figure}
\centering

TODO: commutativity diagram of screenshots with two cursors

TODO: include legend of arrow colors

\caption{TODO:Commutativity}
\label{fig:Commutativity}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureEditingNestedParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{NestedAlice}{L}
\newvertex{NestedAlice}{w}
\newedge{NestedBob}{L}
\newcommand{\figureEditingNestedParts}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Editing Different Parts of the Code-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Editing Different Parts of the Code-c}}}};
%%%%
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-a) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Editing Different Parts of the Code-c-x) to (-2em, 0cm |- fig-Editing Nested Parts of the Code-a);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedAlice" [> "\eNestedAlice"', >alice edge, alice],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-b) [anchor=base] {\strut};
\path [draw,->,bob] (fig-Editing Different Parts of the Code-c-x) to [out=15,in=165] (-2em, 0cm |- fig-Editing Nested Parts of the Code-b);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"', >bob edge] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-c) [anchor=base] {\strut};
\path [draw,->,merge] (fig-Editing Nested Parts of the Code-a) to [out=15,in=165] (-2em, 0cm |- fig-Editing Nested Parts of the Code-c);
\path [draw,->,merge] (fig-Editing Nested Parts of the Code-b) to [out=15,in=165] (-2em, 0cm |- fig-Editing Nested Parts of the Code-c);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-c}
\label{fig:Editing Nested-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"', >merge edge] -> {
    "\vNestedAlice" [> "\eNestedAlice"', >merge edge, merge],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code.
\autoref{fig:Editing Nested Parts of the Code-a}:~\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{\vidDifferentAlice} with \Vertex{\vidNestedAlice}.
\autoref{fig:Editing Nested Parts of the Code-b}:~\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{\vidSimpleTimes} to the left child of \Vertex{\vidWrapPlus}.
\autoref{fig:Editing Nested Parts of the Code-c}:~The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}.}
\label{fig:Editing Nested Parts of the Code}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiChild
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\newcommand{\figureMultiChild}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Editing Nested-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Editing Nested-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-child conflict-a) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Editing Nested-c-x) to (-2em, 0cm |- fig-Multi-child conflict-a);
\end{tikzpicture}
}
\label{fig:Multi-child-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice", >alice edge, alice]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-b) [anchor=base] {\strut};
\path [draw,->,bob] (fig-Editing Nested-c-x) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-b);
\end{tikzpicture}
}
\label{fig:Multi-child-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob", >bob edge, bob]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-c) [anchor=base] {\strut};
\path [draw,->,merge] (fig-Multi-child conflict-a) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-c);
\path [draw,->,merge] (fig-Multi-child conflict-b) to (-2em, 0cm |- fig-Multi-child conflict-c);
\end{tikzpicture}
}
\label{fig:Multi-child-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'anchor=-15] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildAlice" [> "\eMultiChildAlice"anchor=153, >merge edge, merge],
   {},
   "\vMultiChildBob" [> "\eMultiChildBob"anchor=195, >merge edge, merge]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{}
\label{fig:Multi-child-d}
TODO: show UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts.}
\label{fig:Multi-child}
\end{figure*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiParent
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiParentAlice}{R}
\newedge{MultiParentBob}{R}
\newcommand{\figureMultiParent}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Multi-child-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-child-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-parent-a) [anchor=base] {\strut};
\path [draw,->,merge] (fig-Multi-child-c-x) to (-2em, 0cm |- fig-Multi-parent-a);
\end{tikzpicture}
}
\label{fig:Multi-parent-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-b) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Multi-parent-a) to (-2em, 0cm |- fig-Multi-parent-b);
\end{tikzpicture}
}
\label{fig:Multi-parent-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"', >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-c) [anchor=base] {\strut};
\path [draw,->,bob] (fig-Multi-parent-a) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-c);
\end{tikzpicture}
}
\label{fig:Multi-parent-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vNestedAlice" [> "\eMultiParentBob", >bob edge]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-d) [anchor=base] {\strut};
\path [draw,->,merge] (fig-Multi-parent-b) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\path [draw,->,merge] (fig-Multi-parent-c) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\end{tikzpicture}
}
\label{fig:Multi-parent-d}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{\vWrapPlus} [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    b/"\vNestedAlice" [> "\eMultiParentAlice"', >merge edge]
   },
   {}
  }
 },
};
\path [draw,->,merge] (a) to ["\eMultiParentBob",out=-60,in=60,merge edge] (b);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-e) [anchor=base] {\strut};
\path [draw,->,alice] (fig-Multi-parent-d) to (-2em, 0cm |- fig-Multi-parent-e);
\end{tikzpicture}
}
\label{fig:Multi-parent-e}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{}
\label{fig:Multi-parent-f}
TODO: UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts.}
\label{fig:Multi-parent}
\end{figure*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSingleUserCycles
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newedge{SingleCyclePlus}{R}
% \newvertex{SingleCyclePlus}{+}
% \newedge{SingleCycleTimes}{L}
% \newvertex{SingleCycleTimes}{*}
% \newedge{SingleCycleCycle}{R}
% \newcommand{\figureSingleUserCycles}{
% \begin{figure}
% %\hfill
% \hskip0.12\linewidth
% %%%%%%%%
% \begin{subfigure}[t]{0.28\linewidth}
% \centering
% \caption{
% \begin{tikzpicture}[remember picture, overlay]
% \path (-7.5em,0cm) node (fig-Multi-parent-e-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-parent-e}}}};
% %%%%
% \path (0cm,0cm) node (fig-Single-User Cycles-a) [anchor=base] {\strut};
% \path [draw,->,alice] (fig-Multi-parent-e-x) to (-2em, 0cm |- fig-Single-User Cycles-a);
% \end{tikzpicture}
% }
% \label{fig:Single-User Cycles-a}
% \begin{tikzpicture}
% \path (0cm,0cm) graph[graph style] {
%  root[root style] -> {
%   v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
%   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
%     {},
%     {}
%   },
%   {}
%   }
%  }
% };
% \end{tikzpicture}
% \end{subfigure}
% %%%%%%%%
% \hfill
% %%%%%%%%
% \begin{subfigure}[t]{0.28\linewidth}
% \centering
% \caption{
% \begin{tikzpicture}[remember picture, overlay]
% \path (0cm,0cm) node (fig-Single-User Cycles-b) [anchor=base] {\strut};
% \path [draw,->,alice] (fig-Single-User Cycles-a) to (-2em, 0cm |- fig-Single-User Cycles-b);
% \end{tikzpicture}
% }
% \label{fig:Single-User Cycles-b}
% \begin{tikzpicture}
% \path (0cm,0cm) graph[graph style] {
%  root[root style] -> {
%   v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
%   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
%     {},
%     "\vSingleCyclePlus" [> "\eSingleCyclePlus", >alice edge, alice] -> {
%      "\vSingleCycleTimes" [> "\eSingleCycleTimes"', >alice edge, alice] -> {
%       {},
%       {}
%      },
%      {}
%     }
%   },
%   }
%  }
% };
% \end{tikzpicture}
% \end{subfigure}
% %%%%%%%%
% \hfill
% %%%%%%%%
% \begin{subfigure}[t]{0.28\linewidth}
% \centering
% \caption{
% \begin{tikzpicture}[remember picture, overlay]
% \path (0cm,0cm) node (fig-Single-User Cycles-c) [anchor=base] {\strut};
% \path [draw,->,alice] (fig-Single-User Cycles-a) to[out=15,in=165] (-2em, 0cm |- fig-Single-User Cycles-c);
% \end{tikzpicture}
% }
% \label{fig:Single-User Cycles-c}
% \begin{tikzpicture}
% \path (0cm,0cm) graph[graph style] {
%  root[root style] -> {
%   v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
%   v2/"\vSimpleTimes" [> "\eNestedBob"'],
%   {}
%   }
%  }
% };
% \path[draw,->,alice] (v2) to ["\eSingleCycleCycle",out=-60,in=-60,alice edge] (v8);
% \end{tikzpicture}
% \end{subfigure}
% %%%%%%%%
% \hfill{}
% \caption{Single-User Cycles.}
% \label{fig:Single-User Cycles}
% \end{figure}
% }
